Stage Oriented Design of an Intersection Management System Based on Laser Scanner Data

### 2015-11-20 paper01/paper.tex
Added preprocessing paragraph

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{../fig/3/proc_stages.png}
\caption{Dataflow through processing stages in an IMS.}
\label{proc_stages}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{../fig/3/processing_stages_and_tasks.png}
\caption{Processing stages and tasks performed.}
\label{proc_stages_tasks}
\end{figure}

@@

\subsection{Dataset}
 The dataset used for this work was provided by POSS research group
\subsection{Preprocessing}
\subsection{Feature Analysis}
\subsection{Pattern Recognition}
\subsection{Situation Assesment}

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.35]{../fig/3/proc_stages.png}
\caption{Dataflow through processing stages in an IMS.}
\label{proc_stages}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.35]{../fig/3/processing_stages_and_tasks.png}
\caption{Processing stages and tasks performed.}
\label{proc_stages_tasks}
\end{figure}
\subsection{Preprocessing}
 In the preprocessing stage raw data from sensor is received and the purpose is to enhance this data through filtering noise, removing outliers and discarding corrupted data. Also, in order to extract meaningful data, background removal techniques are applied in this stage. For doing this, a background model should be generated. One typical approach to generate a background model is to use a threshold to determine if certain measure corresponds to background or foreground. This threshold is computed based on a peak value found in histogram information of the measure within a time window. Another approach consist in describe de data using a probability distribution function.
\subsection{Feature Analysis}
\subsection{Pattern Recognition}
\subsection{Situation Assesment}

@@

\subsection{Dataset}
 The dataset used for this work was provided by POSS research group and was used for \cite{Zhao2009}. The dataset consist of ten minutes of laser scanner raw data from six sensors arranged horizontally over an intersection near Peking University. Background model and calibration data for each laser scanner is also provided. Additionally, dataset contains trajectory info of objects in the scene, generated by their algorithm.

\subsection{Preprocessing}

\subsection{Feature Analysis}
\subsection{Pattern Recognition}
\subsection{Situation Assesment}
